Hypertension and microbiome

### 2018-12-31 rrbiome.Rmd
Minor

```{r calculate full alpha model}
calculateglm(dset.alpha, modelstring = "%s ~ BL_AGE + SEX + BMI + CURR_SMOKE + ANYEXERCICE + DIAB + ANYDRUG  + diversities_shannon") %>%
    select(response, estimate, std.error, conf.low, conf.high, p.value) %>%
    kable(.)
```

>>>>

```{r calculate binomial alpha model}
calculateglm(dset.alpha, modelstring = "%s ~ BL_AGE + SEX + BMI + CURR_SMOKE + ANYEXERCICE + DIAB + ANYDRUG  + diversities_shannon") %>%
    select(response, estimate, std.error, conf.low, conf.high, p.value) %>%
    kable(.)
```
